Aspects of RDF Data Constraints in the Social, Behavioural and Economic Sciences

### 2015-05-01 paper/paper7/paper7.tex
conclusion

We identified and published by today 82 types of constraints\footnote{The first appendix of this paper, in which we explain each requirement/constraint type in detail, is available at: \url{http://arxiv.org/abs/1501.03933} \cite{BoschNolleAcarEckert2015}}
that are required by various stakeholders for data applications.
In close collaboration with several \emph{SBE} domain experts, we formulated 213 constraints\footnote{The second appendix of this paper, in which we describe each vocabulary-specific constraint in detail, is available at: \url{http://arxiv.org/abs/1504.04479} \cite{BoschZapilkoWackerowEckert2015}}
 of 53 different types on three different vocabularies (\emph{Disco}, \emph{QB}, and \emph{SKOS}) and classified them according to the complexity level of their type and their severity level.

For 114 of these constraints, we evaluated\footnote{The third appendix of this paper, in which we describe the evaluation in detail, is available at: \url{http://arxiv.org/abs/1504.04478} \cite{BoschZapilkoWackerowEckert2015-2}.}
 the data quality of 15,694 data sets (4.26 billion triples) of research data for the \emph{SBE} sciences obtained from 33 SPARQL endpoints.
Based on the evaluation results,
we formulated several hypotheses to direct the further development of constraint languages.
To make valid general statements for all vocabularies, however,
the hypotheses still have to be verified or falsified
by evaluating the quality of data represented by more than three vocabularies.
The main hypotheses are: 
\begin{enumerate}
	\item The percentage of severe violations is very low which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
  \item The further development of constraint languages should concentrate on how to express \emph{complex constraints} as 44\% of all \emph{complex constraints} are also serious ones.
  \item 47\% of the violations refer to complex constraints that are in most cases not expressible by existing constraint languages which confirms the necessity to provide suitable constraint languages.
  \item As 54\% of the constraints are either \emph{simple} or \emph{complex constraints},
the further development of constraint languages should concentrate on expressing \emph{simple} and especially \emph{complex constraints} which up to now in most cases can only be expressed by plain \emph{SPARQL}. 
\end{enumerate}

>>>>

We identified and published by today 82 types of constraints  that are required by various stakeholders for data applications.
In close collaboration with several \emph{SBE} domain experts, we formulated 213 constraints of 53 different types on three different vocabularies (\emph{Disco}, \emph{QB}, and \emph{SKOS}) and classified them according to the complexity level of their type and their severity level.

For 114 of these constraints, we evaluated  the data quality of 15,694 data sets (4.26 billion triples) of research data for the \emph{SBE} sciences obtained from 33 SPARQL endpoints.

Based on the evaluation results,
we formulated several hypotheses to direct the further development of constraint languages. We regard to the results as hypotheses, as their general applicability beyond the examined vocabularies and for other domains is still to be confirmed.

The main hypotheses are: 
\begin{enumerate}
	\item The percentage of severe violations is very low which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
  \item The further development of constraint languages should concentrate on how to express \emph{complex constraints} as 44\% of all \emph{complex constraints} are also serious ones.
  \item 47\% of the violations refer to complex constraints that are in most cases not expressible by existing constraint languages which confirms the necessity to provide suitable constraint languages.
  \item As 54\% of the constraints are either \emph{simple} or \emph{complex constraints},
the further development of constraint languages should concentrate on expressing \emph{simple} and especially \emph{complex constraints} which up to now in most cases can only be expressed by plain \emph{SPARQL}. 
\end{enumerate}

We have been really impressed by the high quality of the \emph{QB} and \emph{SKOS} data. This is in contrast to the sometimes heard rumour that Linked Open Data lacks quality. We are actively involved in the further development and implementation of constraint languages and will use the results presented in the paper to set priorities on features where we expect the highest impact on the data quality of real-life data in the SBE domain.
